### 2016-10-26 doc/publications/plos16/plos16.tex
changes to plos16.tex

\end{flushleft}
\tableofcontents
\clearpage
\section{Notes}
\begin{itemize}
\item I think the structure of the first section should be
  \begin{itemize}
  \item convergence results from Biau 2012  (done)
  \item consider  \cite{Segal.2004} examples
  \item simulations reproduced from Genuer et al 2010 (no -- we need classification examples)
  \item check Piotr's simulation  (done)
  \item run spark ML or CursedForest on the  simulation data 
  \item we extend the simulations to many more variables 
  \item I dont think I can get R to handle chromosme 1 etc. May have to run CF on chromosme 22, see table
    \ref{table:smaller_data} -- On it, Aidan
  \item variable  selection may succeed where accurate prediction does not
  \item discussion of the effect of the \ntree\ and \mtry\ parameters for variable selection with many noise variables
  \item   perhaps we argue that in the case where the relationship of $X$ and $y$ takes a particular form (step, ramp) we can recover
    the significant variables in the presence of a very large number of noise variables
  \item in the case of genomic data, our functions of interest are more likely to be stop or ramp functions rather than harmonic
    functions. So we have some hope.
  \end{itemize}
\item check out 
  \begin{itemize}
  \item D\'iaz-Uriarte, R., \& Alvarez de Andr\'es, S. (2006). (done)
  \item \cite{Goldstein.et.al.2011}
notes that the 0, 1, 2 encoding of alleles is an additive model i.e. each additional minor allele increases the effect 
\begin{verbatim}
Different genetic effects
Type	Mechanism	Partition
Additive	Each additional minor allele increases variation	0, 1, 2
Dominant	Presence of at least 1 minor allele increases variation	0, 1/2
Recessive	Two minor alleles needed for variation	0/1, 2
Heterosis	Heterozygote leads to variation	0/2, 1
\end{verbatim}

  \item Chen (2012)  (done)
  \item VSURF and  varSelRF, (done) recursive feature (forwards backwards) using variable importance
  \item \cite{Wright.and.Ziegle.2016} ranger package (doing it!)
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest
    Implementation for Biological Data
   Ensembles of decision trees in go/golang   --  do we need to look
   at this? 
  \item \cite{Tuv.et.al.2009} feature selection via adding permuted variables. Do we want to consider this? (no, leave it for now)
  \end{itemize}
\item other things to do
  \begin{itemize}
  \item what is the problem with bagging? Do we need to redo the thousand genome stuff?
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \ntree\ the number of trees.  The number of trees necessary for good performance grows with the number of predictors.
  \marginpar{can we do proximity?} \cite{Liaw.and.Weiner.2002} suggest that a high \ntree\ is necessary to get stable
  estimates of variable importance and proximity; however, even though the variable importance measures may vary from run to run,
  the ranking of the importances is quite stable.  In addition, we note that it is possible for a random forest model to have a very poor
  fit, and be useless for prediction, and still have a useful ranking of variable importance.
\item \mtry\ -- the number of variables considered at each split (if \mtry=$p$, we have a boosted decision
  tree model).  If one has a very large number of variables but expects only very few to be ``important'', using larger \mtry\ may give
  better performance.
\item For classification problems where the class frequencies are extremely unbalanced it may be necessary to change the prediction
  rule \marginpar{can we do this}
\item the size and complexity of the individual trees is controlled in {\sc randomForest} by setting \texttt{nodesize}, the
  minimum size of terminal nodes. It is controlled in Spark ML by setting \texttt{maxDepth}, the maximum depth of each
  tree in the forest. The Spark ML documentation sets \texttt{maxDepth} to 4 in their classification
  example\footnote{The documentation is available at \url{http://spark.apache.org/docs/latest/mllib-ensembles.html}.}.

@@

Figure~\ref{figure:synth}b illustrates that increasing \mtry\ also improves the OOB (out of bag) classification error.
%Piotr can you please explain the remaining error on the synthetic data
By $mtry=0.8$ the error is converging to X, which is due to Y.

>>>>

\end{flushleft}
\tableofcontents
\clearpage

@@

\begin{itemize}
\item \ntree\ the number of trees.  The number of trees necessary for good performance grows with the number of predictors.
  \marginpar{can we do proximity?} \cite{Liaw.and.Weiner.2002} suggest that a high \ntree\ is necessary to get stable
  estimates of variable importance and proximity; however, even though the variable importance measures may vary from run to run,
  the ranking of the importances is quite stable.  In addition, we note that it is possible for a random forest model to have a very poor
  fit, and be useless for prediction, and still have a useful ranking of variable importance.
\item \mtry\ -- the number of variables considered at each split (if \mtry=$p$, we have a boosted decision
  tree model).  If one has a very large number of variables but expects only very few to be ``important'', using larger \mtry\ may give
  better performance.
\item For classification problems where the class frequencies are extremely unbalanced it may be necessary to change the prediction
  rule \marginpar{can we do this}
\item the size and complexity of the individual trees is controlled in {\sc randomForest} by setting \texttt{nodesize}, the
  minimum size of terminal nodes. It is controlled in Spark ML by setting \texttt{maxDepth}, the maximum depth of each
  tree in the forest\footnote{The Spark ML documentation \cite[]{Spark.2016} sets \texttt{maxDepth}
    to 4 in their classification example. This is wrong. The
    individual trees should be grown to a large size to ensure that
    they give an unbiased estimate.}.

@@

\marginpar{wrong figure cited}
Figure~\ref{figure:synth}b illustrates that increasing \mtry\ also improves the OOB (out of bag) classification error.
%Piotr can you please explain the remaining error on the synthetic data
By $mtry=0.8$ the error is converging to X, which is due to Y.
